---
title: "sghorui_OriginalHomeworkCode_01"
author: "Soumalya"
format: html
editor: visual
---

# Module 4: Working with Other Data Structure

Installing package [stringr](https://cran.r-project.org/web/packages/stringr/stringr.pdf)

```{r}
install.packages("stringr")
```

## Challenge 1

-   First, create a vector of 1, word character strings comprising the first line of the novel *Ulysses*, by James Joyce: “Stately, plump Buck Mulligan came from the stairhead, bearing a bowl of lather on which a mirror and a razor lay crossed.”

    ```{r}
    u<-c("Stately","plump","Buck","Mulligan","came","from","the","stairhead","bearing","a","bowl","of","lather","on","which","a","mirror","and","a","razor","lay","crossed") #creating the vector
    u #displaying the result
    ```

Then, extract every third element of this vector.

-   **HINT 1:** Take a look at the {stringr} package and the function `str_split()` to see if you can easily divide a single string into a vector of substrings.

```{r}
u[c(3,6,9,12,15,18,21)] #writing their index number(positions) within the vector to extract them.
```

```{r}
m <- matrix(data = 1:80, nrow = 8, ncol = 10, byrow = FALSE)
m
```

### Overwriting

```{r}
m[7, 1] <- 564
m
```

```{r}
m[, 8] <- 2
m
```

```{r}
m[2:5, 4:8] <- 1
m
```

```{r}
m[2:5, 4:8] <- c(20, 19, 18, 17)
m
```

```{r}
m[2:5, 4:8] <- matrix(data = c(20:1), nrow = 4, ncol = 5, byrow = TRUE)
m
```

```{r}
m[, 8] <- c("a", "b")
m
```

## Challenge 2

-   Given the matrix, **m**, above, extract the 2nd, 3rd, and 6th columns and assign them to the variable **x**

-   Given the matrix, **m**, above, extract the 6th to 8th row and assign them to the variable **x**

-   Given the matrix, **m**, above, extract the elements from row 2, column 2 to row 6, column 9 and assign them to the variable **x**

```{r}
x <- m[,c(2, 3, 6)] #extracting the 2nd, 3rd, and 6th columns from m,assigned them to the variable x
x
```

```{r}
x <- m[,c(6,8)] #Given the matrix, m, above, extract the 6th to 8th row and assign them to the variable x
x
```

```{r}
x <- m[c(2,3,4,5,6),c(2,3,4,5,6,7,8,9)] #Given the matrix, m, above, extract the elements from row 2, column 2 to row 6, column 9 and assign them to the variable x
x
```

## **Challenge 3**

-   Construct a 4-dimensional, 400 element array (5 x 5 x 4 x 4) named **a** consisting of the numbers 400 to 1 (i.e., a descending series).

    ```{r}
    a <- array(data = 400:1, dim = c(5,5,4,4)) #creating a 4D array
    a
    ```

<!-- -->

-   Given this matrix, what would the following return?

    -   a\[1, 1, 1, 2\]

    -   a\[2, 3, 2, \]

    -   a\[1:5, 1:5, 3, 3\]

    ```{r}
    a[1, 1, 1, 2]
    ```

```{r}
a[2, 3, 2, ]
```

```{r}
a[1:5, 1:5, 3, 3]
```

## Challenge 4

Create a **list** representing this (simplified) primate taxonomy:

-   Primates

    -   Haplorhini

        -   Anthropoidea

            -   Platyrrhini

                -   Cebidae

                -   Atelidae

                -   Pitheciidae

            -   Catarrhini

                -   Cercopithecidae

                -   Hylobatidae

                -   Hominidae

        -   Tarsioidea

            -   Tarsiidae

    -   Strepsirhini

        -   Lorisoidea

            -   Lorisidae

            -   Galagidae

        -   Lemuroidea

            -   Cheirogaleidae

            -   Lepilemuridae

            -   Indriidae

            -   Lemuridae

            -   Daubentoniidae

```{r}
Platyrrhini <- c("Cebidae","Atelidae","Pitheciidae") #going from left to right, doing this list first and then the next upper order
Catarrhini <- c("Cercopithecidae","Hylobatidae","Hominidae")
Tarsioidea <- c("Tarsiidae")
Anthropoidea <- list(Platyrrhini, Catarrhini) #listing the next level
names(Anthropoidea) <- list("Platyrrhini", "Catarrhini") #naming them so that they shows the names of the given list under each of them
names(Tarsioidea) <- list("Tarsioidea")
Haplorhini <- list(Anthropoidea, Tarsioidea)
names(Haplorhini) <- list("Anthropoidea", "Tarsioidea")
Lemuroidea <- c("Cheirogaleidae", "Lepilemuridae", "Indriidae", "Lemuridae", "Daubentoniidae") #repeating the process
Lorisoidea <- c("Lorisidae", "Galagidae")
Strepsirhini <- list(Lemuroidea, Lorisoidea)
names(Strepsirhini) <- list("Lemuroidea", "Lorisoidea")
Primates <- list(Haplorhini, Strepsirhini)
names(Primates) <- list("Haplorhini", "Strepsirhini")
Primates
```

## Challenge 5

-   Store the following numbers as a 5 x 3 matrix, called “m3”: 3, 0, 1 ,23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2. Be sure to fill the matrix ROW-WISE.

-   Then, do the following:

    -   Coerce the matrix to a data frame.

    -   As a data frame, coerce the second column to be *logical-valued*

    -   As a data frame, coerce the third column to be *factor-valued*

When you are done, use the `str()` command to show the data type for each variable in your dataframe.

```{r}
m3 <- matrix(c(3, 0, 1, 23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2), 
             nrow = 5, ncol = 3, byrow = TRUE)
m3
```

```{r}
df <- as.data.frame(m3)
df
```

```{r}
df[[2]] <- as.logical(df[[2]])
df
```

```{r}
df[[3]] <- as.factor(df[[3]])
df
```

```{r}
str(df)
```
